Parameterless Population Pyramid

### 2013-09-11 Parameterless Population Pyramid/main.tex
Outline of P3 paper, some citations

\documentclass{sig-alternate}
%\linespread{2.5}
\usepackage{url}
\usepackage{verbatim}
\newcommand{\includegraphicsfit}[1]
{\includegraphics[width=\columnwidth,height=\textheight,keepaspectratio]{#1}}
\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{GECCO'14,} {July 12--16, 2014, Vancouver, BC, Canada.}
\CopyrightYear{2014}
\crdata{978-1-4503-1963-8/13/07}
\clubpenalty=10000
\widowpenalty = 10000
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\maketitle
\begin{abstract}

\end{abstract}

@@

\section{Introduction}
TODO~\cite{goldman:2012:ltga}.

>>>>

\documentclass{sig-alternate}
%\linespread{2.5}
\usepackage{url}
\usepackage{verbatim}
\newcommand{\includegraphicsfit}[1]
{\includegraphics[width=\columnwidth,height=\textheight,keepaspectratio]{#1}}

\usepackage{bm}
\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{GECCO'14,} {July 12--16, 2014, Vancouver, BC, Canada.}
\CopyrightYear{2014}
\crdata{978-1-4503-1963-8/13/07}
\clubpenalty=10000
\widowpenalty = 10000
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\maketitle
\begin{abstract}
TODO
\end{abstract}

@@

\section{Introduction}
TODO Parameterless optimization, model building, etc.

\section{The P3 Algorithm}
TODO Overview.  Use graphic.

\subsection{Hill Climber}
TODO Describe First Improvement Hill Climber, including waste prevention, etc.

\subsection{Pyramid}
TODO Explain population levels, entropy tables $O(n^2)$, uniqueness

\subsection{Crossover}
TODO Explain how entropy becomes clusters efficiently $O(n^2)$, cluster ordering,
keep changes that don't reduce fitness, removal of zero entropy sub-clusters,
keep donating until a change is made.

\subsection{All Together}
TODO Pieces working together.  HC removes pairwise noise, which allows crossover to detect
clusters.  Levels allow realization of linkage at high levels, reduction in noise.

\section{Comparison Algorithms}

\subsection{Random Restart First Improvement Hill Climber}
TODO This is important to have as it shows how the pyramid is able to reach optima
the hill climber cannot.  Need a citation.

\subsection{Linkage Tree Genetic Algorithm}
TODO Discuss LTGA~\cite{thierens:2013:ltgahiff}, how it differs from P3, its limitation based on
initialization, requirement of population size.  Mention how some
of the ideas in P3 were tried in LTGA and seemed to make improvements~\cite{goldman:2012:ltga}.
Discuss bisection method and Rule of Three~\cite{jovanovic:1997:ruleofthree}.
Remember to say that the paper argues for $\frac{3}{N+1}$, so 100 trails is strictly
less than $3\%$ expected failure rate.

\subsection{\bm{$(1+(\lambda,\lambda))$}}
TODO Explain briefly how it works, that it is the best theory supported crossover method~\cite{doerr:2013:lambdalambda}.
Explain changes including: Keep best mutant if no worse than crossover offspring,
prevent evaluations if crossover offspring identical to either parent, if tied fitness
in crossover offspring take maximum hamming distance to parent.  If $\lambda \ge N$
restart with random individual.  Does not use ``mod'' version as restarting is preferable
when stuck on plateaus.

\section{Test Problems}

\subsection{Single Instance Problems}
TODO Deceptive Trap, Deceptive Step Trap~\cite{goldman:2012:ltga}, Hierarchical If
and Only If, Discretized Rastrigin.

\subsection{Randomly Generated Problem Classes}
TODO Nearest Neighbor NK with wrapping neighborhoods, Ising Spin Glasses on toroidal
grids with only -1, 1 spins, Maximum Satisfiability constructed with known global
optimum.

\section{Experimental Results}
TODO Cover all 7 problems as a group, focusing on the two ``types'' of problems.
Make it explicit that you outperform by a constant factor on the static problems
and by an order of complexity on generated problems.

TODO Include graphic for 7 problem results.

TODO Include table comparing results on largest version of each problem.

\section{Promising Theory}
TODO Easy proof on unimodal (no plateaus) and all functions of unitation due to HC.
Sketch of how to prove runtime on Deceptive Trap, HIFF, suggestions toward all
possible non-overlapping functions.

\section{Conclusions and Future Work}
TODO No parameters required, beats tuned LTGA.  Good at solving hard classes
of problems, not just single instances of a problem as it scales to problem difficulty.
Future work in theory.  Also readily applicable to real world problems as no
problem information is required.
